Methods for Large Scale Learning to Rank

### 2014-04-10 report/Chapters/CrossBenchmarkComparison.tex
cross benchmark comparison

C-CRF, DirectRank, FP-Rank, RankCSA, LambdaNeuralRank and VFLR all have near-perfect Normalised Winning Number measures, but have low Ideal Winning Number measures. Further evaluation runs of these methods on benchmark datasets that they are not yet evaluated on are desirable. The DirectRank paper \cite{Tan2013} shows that the method actually is evaluated datasets than is used in this paper. however measurements on some datasets were only available in graphical form and not in raw data, making these measurements unusable for this comparison.

@@

>>>>

C-CRF, DirectRank, FP-Rank, RankCSA, LambdaNeuralRank and VFLR all have near-perfect Normalised Winning Number measures, but have low Ideal Winning Number measures. Further evaluation runs of these methods on benchmark datasets that they are not yet evaluated on are desirable. The DirectRank paper \cite{Tan2013} shows that the method actually is evaluated datasets than is used in this paper. however measurements on some datasets were only available in graphical form and not in raw data, making these measurements unusable for this comparison.\\

LAC-MR-OR and RE-QR showed very good ranking accuracy in the \ac{MAP} comparison on multiple datasets. Both methods Because LAC-MR-OR is only evaluated on two datasets for \ac{nDCG}@10 and RE-QR is not evaluated for \ac{nDCG} at all

@@

In the following chapters of this thesis, concerning parallel execution of the Learning-to-Rank training phase, the scope will be limited to the five methods that turned out to be superior Learning-to-Rank methods in terms of ranking accuracy and certainty about this ranking accuracy: LRUF, FSMRank, FenchelRank, SmoothRank and ListNet. Although it can not be concluded that these methods are inarguably the most accurate Learning-to-Rank methods, a strong presumption has been raised that these five Learning-to-Rank are accurate ranking methods.
